Properties of coronal Fourier power spectra and their implications for coronal seismology and coronal heating.

### 2014-05-02 tex/paper1/paper1.tex
fixed AIA 171 loop foot point results
edits to the model fitting appendix

%\begin{figure}
%\label{fig:fit193}
%\plottwo{}{}
%\plottwo{}{}
%
%\caption{}
%\end{figure}
\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.\label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{power law} & \multicolumn{3}{c}{Gaussian} \\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$ (mHz)}      &
\colhead{$\sigma$}
}
\startdata
loop footpoints & 171\AA  & $0.47^{+0.01}_{-0.01}$  &$1.86^{+0.01}_{-0.01}$  & $-3.97^{+0.00}_{-0.00}$  & $-1.333^{0.02}_{-0.02}$ & $1.05^{+0.02}_{-0.02}$  & $0.31^{+0.03}_{-0.03}$  \\
                & 193\AA  &   & 0 & 0  & 0  & 0  & 0  \\

@@

The results for the quiet Sun, loop footpoints and sunspot regions
suggest a power-law power spectrum.  This can be modeled as
\begin{equation}
\label{eq:pwrlaw}
\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
\end{equation}
where $A>0$ is a proportionality constant and $n>0$ is the power law
index.  The quantity $C>0$ models the high-frequency / low power end
of the spectrum where the detection properties of the detector
apparatus are assumed to dominate the observations.

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of Fourier power.  This suggests that a second model $M_{2}$ for these
regions should be considered.  The second model $M_{2}$ has two
contributions to the overall \Fps; a background power-law of the form
of $P_{1}$, and a contribution that is more localized, $G(\nu)$.  The
model is given by
\begin{equation}
\label{eq:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions.  Figures
\ref{fig:fit171} and \ref{fig:fit193} show the best fit results of
each model to the data (for details on the fitting procedure, see
Section \ref{sec:app:ind}).

@@

\section{Model fitting procedure}\label{sec:app:ind}

Figures \ref{} show that the logarithm of the Fourier power in a
region of the Sun may be approximated by a normal distribution $N(\mu,
\sigma)$.  The
maximum likelihood estimate of the mean and variance of normal
distribution are given by
\begin{equation}
\hat{\mu} = \frac{1}{N}\sum_{i=1}^{N}X_{i}
\label{eqn:mlmean}
\end{equation}
and
\begin{equation}
\hat{\sigma^{2}} = \frac{1}{N}\sum_{i=1}^{N}(X_{i}-\mu)^{2}
\label{eqn:mlmean}
\end{equation}
where $N$ is the number of independent measurements.  The estimated
error in the estimated error is
\begin{equation}
\sqrt{\hat{\sigma^{2}}}/\sqrt{N}
\label{eqn:mlmean}
\end{equation}

>>>>

%\begin{figure}
%\label{fig:fit193}
%\plottwo{}{}
%\plottwo{}{}
%
%\caption{}
%\end{figure}
\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.\label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{power law} & \multicolumn{3}{c}{Gaussian} \\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$ (mHz)}      &
\colhead{$\sigma$}
}
\startdata
loop footpoints & 171\AA  & $0.65^{+0.02}_{-0.02}$  &$2.27^{+0.02}_{-0.02}$  & $-4.15^{+0.00}_{-0.00}$  & $-2.16^{0.12}_{-0.11}$ & $0.64^{+0.10}_{-0.10}$  & $0.33^{+0.02}_{-0.02}$  \\
                & 193\AA  &   & 0 & 0  & 0  & 0  & 0  \\

@@

The results for the quiet Sun, loop footpoints and sunspot regions
suggest a power-law power spectrum.  This can be modeled as
\begin{equation}
\label{eq:pwrlaw}
\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
\end{equation}
where $\nu$ is the normalized frequency, $A>0$ is a proportionality
constant and $n>0$ is the power law index.  The quantity $C>0$ models
the high-frequency / low power end of the spectrum where the detection
properties of the detector apparatus are assumed to dominate the
observations.

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of Fourier power.  This suggests that a second model $M_{2}$ for these
regions should be considered.  The second model $M_{2}$ has two
contributions to the overall \Fps; a background power-law of the form
of $P_{1}$, and a contribution that is more localized, $G(\nu)$.  The
model is given by
\begin{equation}
\label{eq:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions.  Figures
\ref{fig:fit171} and \ref{fig:fit193} show the fit results of
each model to the data.  Table \ref{tab:parameters} shows the fitted
parameter values and an error estimate for model $M_{2}$.  For details
on the fitting procedure, see Section \ref{sec:app:ind}.

@@

\section{Model fitting procedure}\label{sec:app:ind}
Equations \ref{pwrlaw} and \ref{pwrlawbump} are fit to the geometric
mean power spectra shown in Figures \ref{fig:fit171} and
\ref{fig:fit193}.  The frequency $\nu$ is defined as $f/f_{0}$ where
$f$ is the FFT frequency in Hz, and $f_{0}$ is the lowest non-zero FFT
frequency defined by the data (Section \ref{sec:obs}).

Figures \ref{fig:dist171} and \ref{fig:dist193} show that the
logarithm of the Fourier power in a region of the Sun may be
approximated by a normal distribution $N(\mu, \sigma)$.  The maximum
likelihood estimate of the mean and variance of normal distribution
are given by
\begin{equation}
\hat{\mu} = \frac{1}{N}\sum_{i=1}^{N}X_{i}
\label{eqn:mlmean}
\end{equation}
and
\begin{equation}
\hat{\sigma^{2}} = \frac{1}{N}\sum_{i=1}^{N}(X_{i}-\mu)^{2}
\label{eqn:mlmean}
\end{equation}
where $N$ is the number of independent measurements.  The estimated
error in the estimated error is
\begin{equation}
\sqrt{\hat{\sigma^{2}}}/\sqrt{N}
\label{eqn:mlmean}
\end{equation}
